---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SIVA

<!-- badges: start -->
[![R-CMD-check](https://github.com/cedricbriandgithub/SIVA/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/cedricbriandgithub/SIVA/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

L'objectif du package SIVA est de fournir les outils de requetage de la base de données SIVA, et les principaux graphiques permettant l'exploitation du barrage d'Arzal et la gestion des inondations.

## Installation

You can install the development version of SIVA from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cedricbriandgithub/SIVA")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
#library(SIVA)
## TODO basic example code
```


```{r connection db}
#TODO 
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
#TODO plot
```

## Code de conduite

Veuillez noter que le projet SIVA suit le code de conduite des contributeurs [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). En contribuant à ce projet, vous acceptez d'en respecter les termes.


