---
title: "databasetools.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```


```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

<!-- TODO generate examples dev -->


# Tablesiva

La classe Tablesiva contient toutes les données pour identifier la table, aller la chercher à l'aide de la méthode RequeteODBCwhere du package stacomirtools.
Elle possède aussi les méthodes décrites ci-dessous.
    
```{r class-Tablesiva}
#' Class for SIVA connexion
#' 
#' 
#' 
#' @return
#' 
#' @export
Tablesiva <- function(){
    
}
```
  
```{r example-Tablesiva}
Tablesiva()
```
  
```{r tests-Tablesiva}
test_that("Tablesiva works", {
  expect_true(inherits(Tablesiva, "function")) 
})
```
  


<!--
Create a chunk with an example of use for your function

- The chunk needs to be named `examples` at least
- It contains working examples of your function
- The chunk is better be named `examples-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This example will automatically be added in the '@examples' part of our function above in the "R/" directory
- This example will automatically be added in the vignette created from this Rmd template
-->

```{r examples}
my_median(1:12)

# Example with your dataset in "inst/"
datafile <- system.file("nyc_squirrels_sample.csv", package = "SIVA2")
nyc_squirrels <- read.csv(datafile, encoding = "UTF-8")
# Apply my function
my_median(nyc_squirrels[,"hectare_squirrel_number"])
```

<!--
Create a chunk with a test of use for your function

- The chunk needs to be named `tests` at least
- It contains working tests of your function
- The chunk is better be named `tests-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This test code will automatically be added in the "tests/testthat/" directory
-->

```{r tests}
test_that("my_median works properly and show error if needed", {
  expect_true(my_median(1:12) == 6.5)
  expect_error(my_median("text"))
})

# Test with your dataset in "inst/"
datafile <- system.file("nyc_squirrels_sample.csv", package = "SIVA2")
nyc_squirrels <- read.csv(datafile, encoding = "UTF-8")
# Apply test on my function
test_that("my_median works properly with internal dataset", {
  expect_equal(my_median(nyc_squirrels[,"hectare_squirrel_number"]), 3)
})
```

# Calculate the mean of a vector

<!--
There can be other functions, examples and tests in your flat template.
Each of them will be inflated in a different file, provided that there is a level-1 or level-2 section title to separate from previous functions.
-->

## Use sub-functions in the same chunk

```{r function-my_other_median}
#' My Other median
#'
#' @param x Vector of Numeric values
#' @inheritParams stats::median
#'
#' @return
#' Median of vector x
#' @export
#'
#' @examples
my_other_median <- function(x, na.rm = TRUE) {
  if (!is.numeric(x)) {stop("x should be numeric")}
  sub_median(x, na.rm =na.rm)
}

#' Core of the median not exported
#' @param x Vector of Numeric values
#' @inheritParams stats::median
sub_median <- function(x, na.rm = TRUE) {
  stats::median(x, na.rm)
}
```

```{r examples-my_other_median}
my_other_median(1:12)
```

```{r tests-my_other_median}
test_that("my_median works properly and show error if needed", {
  expect_true(my_other_median(1:12) == 6.5)
  expect_error(my_other_median("text"))
})
```

<!--
# There can be development actions

Create a chunk with 'development' actions

- The chunk needs to be named `development` or `dev`
- It contains functions that are used for package development only
- Note that you may want to store most of these functions in the 0-dev_history.Rmd file

These are only included in the present flat template file, their content will not be part of the package anywhere else.
-->

```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_full.Rmd", vignette_name = "Get started")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
